---
title: "p8105_hw6_dk2759"
author: "Darwin Keung"
date: "11/25/2018"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(modelr)
#set.seed(1)
```

http://p8105.com/homework_6.html

-------
Homework 6
Context
This assignment reinforces ideas in Linear Models.

Due date
Due: November 27 at 11:00pm.

Points
Problem 0: 20 points
Problem 1: 30 points
Problem 2: 50 points
Problem 0
This “problem” focuses on structure of your submission, especially the use git and GitHub for reproducibility, R Projects to organize your work, R Markdown to write reproducible reports, relative paths to load data from local files, and reasonable naming structures for your files.

To that end:

create a public GitHub repo + local R Project for this assignment
write solutions using a .Rmd file that outputs a github_document / .md file
submit a link to your repo via Courseworks
Your solutions to Problems 1 and 2 should be implemented in your .Rmd file, and your git commit history should reflect the process you used to solve these Problems.

For Problem 0, we will assess adherence to the instructions above regarding repo structure, git commit history, and whether we are able to knit your .Rmd to ensure that your work is reproducible. Adherence to appropriate styling and clarity of code will be assessed in Problems 1+ using the homework style rubric.

This homework includes figures; the readability of your embedded plots (e.g. font sizes, axis labels, titles) will be assessed in Problems 1+.

## Problem 1

The _Washington Post_ has gathered data on homicides in 50 large U.S. cities and made the data available through a GitHub repository [here](https://github.com/washingtonpost/data-homicides). You can read their accompanying article [here](https://www.washingtonpost.com/graphics/2018/investigations/where-murders-go-unsolved/). 

---------

#### Data import and cleaning

Created city_state variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved. Omitted cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omitted Tulsa, AL – this is a data entry mistake. Modifiy victim_race to have categories white and non-white, with white as the reference category. Be sure that victim_age is numeric.

```{r import}
homicide_df = read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv", col_names = TRUE) %>%
  janitor::clean_names() %>% 
  mutate(city_state = str_c(city, ",", "", state),
         solved = if_else(disposition == "Closed by arrest", "resolved", "unresolved"),
         solved = fct_relevel(solved, "unresolved"),
         victim_age = as.numeric(victim_age),
         victim_race = tolower(victim_race),
         victim_race = ifelse(victim_race == "white", "white", "non-white"),
         victim_race = fct_relevel(victim_race, "white")) %>%
  filter(!(city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL")))
```



The homicide dataset contains data collected from 50 big US cities over the a decade. It has `r nrow(homicide_df)` rows and `r ncol(homicide_df)` columns. The variables include a unique id, report date, first and last names of victims, age, sex, race, location (city, state, lat, long), and disposition. 


Create a city_state variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved. Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL – this is a data entry mistake. Modifiy victim_race to have categories white and non-white, with white as the reference category. Be sure that victim_age is numeric.



For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race (as just defined) as predictors. Save the output of glm as an R object; apply the broom::tidy to this object; and obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing non-white victims to white victims keeping all other variables fixed.

Now run glm for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing non-white victims to white victims. Do this within a “tidy” pipeline, making use of purrr::map, list columns, and unnest as necessary to create a dataframe with estimated ORs and CIs for each city.

Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.

Problem 2
In this probelm, you will analyze data gathered to understand the effects of several variables on a child’s birthweight. This dataset, available here, consists of roughly 4000 children and includes the following variables:

babysex: baby’s sex (male = 1, female = 2)
bhead: baby’s head circumference at birth (centimeters)
blength: baby’s length at birth (centimeteres)
bwt: baby’s birth weight (grams)
delwt: mother’s weight at delivery (pounds)
fincome: family monthly income (in hundreds, rounded)
frace: father’s race (1= White, 2 = Black, 3 = Asian, 4 = Puerto Rican, 8 = Other, 9 = Unknown)
gaweeks: gestational age in weeks
malform: presence of malformations that could affect weight (0 = absent, 1 = present)
menarche: mother’s age at menarche (years)
mheigth: mother’s height (inches)
momage: mother’s age at delivery (years)
mrace: mother’s race (1= White, 2 = Black, 3 = Asian, 4 = Puerto Rican, 8 = Other)
parity: number of live births prior to this pregnancy
pnumlbw: previous number of low birth weight babies
pnumgsa: number of prior small for gestational age babies
ppbmi: mother’s pre-pregnancy BMI
ppwt: mother’s pre-pregnancy weight (pounds)
smoken: average number of cigarettes smoked per day during pregnancy
wtgain: mother’s weight gain during pregnancy (pounds)
Load and clean the data for regression analysis (i.e. convert numeric to factor where appropriate, check for missing data, etc.).

Propose a regression model for birthweight. This model may be based on a hypothesized structure for the factors that underly birthweight, on a data-driven model-building process, or a combination of the two. Describe your modeling process and show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.

Compare your model to two others:

One using length at birth and gestational age as predictors (main effects only)
One using head circumference, length, sex, and all interactions (including the three-way interaction) between these
Make this comparison in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate.

Note that although we expect your model to be reasonable, model building itself is not a main idea of the course and we don’t necessarily expect your model to be “optimal”.

---------

#### Data import

Describe the raw data:

These data have `r nrow(homicide_df)` rows and `r ncol(homicide_df)` columns. The variables include a unique id, report date, first and last names of victims, age, sex, race, location (city, state, lat, long), and disposition. 

### Binary outcome

Extract data

```{r}
baltimore_df = 
  read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv") %>% 
  filter(city == "Baltimore") %>% 
  mutate(resolved = as.numeric(disposition == "Closed by arrest"),
         victim_age = as.numeric(victim_age),
         victim_race = fct_relevel(victim_race, "White")) %>% 
  select(resolved, victim_age, victim_race, victim_sex)
```

Fit the model 

```{r}
fit_logistic = 
  glm(resolved ~ victim_age + victim_race, 
    data = baltimore_df, 
    family = binomial())
```

Summarize fit

```{r, eval}
summary(fit_logistic)
```

Summarize fit

```{r}
fit_logistic %>% 
  broom::tidy() %>% 
  mutate(OR = boot::inv.logit(estimate)) %>% 
  knitr::kable(digits = 3)
```


```{r}
baltimore_df %>% 
  ggplot(aes(x = victim_age, y = resolved)) + geom_point() + geom_smooth()
```